---
title: "statr"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Alternatively, check out the [vignette](https://htmlpreview.github.io/?https://github.com/MGallow/statr/blob/master/Vignette.html) or [manual](https://github.com/MGallow/statr/blob/master/statr.pdf).

## Overview

`statr` is a personal R package that I have created for organizational/convenience purposes. A (possibly incomplete) list of functions contained in the package can be found below:

* `tidy()` tidy's R package code and updates documentation
* `timeit()` prints the computation time of a function
* `scatter()` creates a scatterplot using ggplot
* `dsearch()` is a dichotomous search algorithm for minimizing a univariate function
* `bsearch()` is a bi-section search algorithm for minimizing a univariate function
* `linearr()` computes the linear regression coefficient estimates (ridge regularization and weights optional)
* `predict_linearr()` generates predictions and loss metric for linear regression
* `logisticr()` computes the coefficient estimates for logistic regression (ridge and bridge regularization optional)
* `predict_logisticr()` generates predictions and loss metrics for logistic


## Installation

The easiest way to install is from the development version from Github:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("MGallow/statr")
```

If there are any issues/bugs, please let me know: [github](https://github.com/MGallow/statr/issues). You can also contact me via my [website](http://users.stat.umn.edu/~gall0441/). Contributions are welcome!


## Usage

```{r, message = FALSE}
library(statr)

#we will use the iris data set
X = dplyr::select(iris, -c(Species, Sepal.Length))
y = dplyr::select(iris, Sepal.Length)
y_class = ifelse(dplyr::select(iris, Species) == "setosa", 1, 0)

#plot Sepal.Length v Sepal.Width
scatter(iris, Sepal.Length, Sepal.Width)

#ridge regression
linearr(X, y, lam = 0.1)

#ridge logistic regression (IRLS)
logisticr(X, y_class, lam = 0.1, penalty = "ridge")

#ridge logistic regression (MM)
logisticr(X, y_class, lam = 0.1, penalty = "ridge", method = "MM")

#bridge logistic regression (MM)
fit = logisticr(X, y_class, lam = 0.1, alpha = 1.2, penalty = "bridge")
fit

#time bridge logistic regression
timeit(logisticr(X, y_class, lam = 0.1, alpha = 1.2, penalty = "bridge"))

#predict using bridge logistic regression estimates
predict_logisticr(fit, X[1:3,], y_class[1:3])
```
