---
title: "statr"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

[![Build Status](https://travis-ci.org/MGallow/statr.svg?branch=master)](https://travis-ci.org/MGallow/statr)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/statr)](https://cran.r-project.org/package=statr)

## Overview

`statr` is a personal R package that I have created for organizational/convenience purposes. This project is purely experimental! A (possibly incomplete) list of functions contained in the package can be found below:

* `tidy()` tidy's R package code and updates documentation
* `timeit()` prints the computation time of a function
* `scatter()` creates a scatterplot using ggplot
* `diagnostic()` creates diagnostic plots using ggplot (residual and QQ)
* `dsearch()` is a dichotomous search algorithm for minimizing a univariate function
* `bsearch()` is a bi-section search algorithm for minimizing a univariate function

See [vignette](https://mgallow.github.io/statr/) or [manual](https://github.com/MGallow/statr/blob/master/statr.pdf).

## Installation

The easiest way to install is from the development version from Github:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("MGallow/statr")
```

If there are any issues/bugs, please let me know: [github](https://github.com/MGallow/statr/issues). You can also contact me via my [website](https://mgallow.github.io/). Contributions are welcome!


## Usage

```{r, message = FALSE}
library(statr)
library(magrittr)

#we will use the iris data set
X = dplyr::select(iris, -c(Species, Sepal.Length))
y = dplyr::select(iris, Sepal.Length)
y_class = ifelse(dplyr::select(iris, Species) == "setosa", 1, 0)

#plot Sepal.Length v Sepal.Width
iris %>% scatter(Sepal.Length, Sepal.Width)

#plot diagnostic plots
iris %>% diagnostic(Sepal.Length, Sepal.Width)


```
