---
title: "statr"
author: "Matt Galloway"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## DOCUMENTATION IN PROGRESS (longer version of README)***

## Overview

`statr` is a personal R package that I have created for organizational/convenience purposes. A (possibly incomplete) list of functions contained in the package can be found below:

* `ridge()` calculate coefficient estimates for ridge (L2)-penalized linear regression
* `bsearch()` is a bi-section search algorithm.



## Installation

```{r, eval = FALSE}
# The easiest way to install is from the development version from GitHub:
# install.packages("devtools")
devtools::install_github("MGallo/statr")
```

If there are any issues/bugs, please let me know: [github](https://github.com/MGallow/statr/issues). You can also contact me via my [website](http://users.stat.umn.edu/~gall0441/).

## Usage

```{r, message = FALSE}
library(statr)

#IN PROGRESS
```
