---
title: "Tutorial"
author: "Matt Galloway"
#date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial}
  %\VignetteEngine{knitr::knitr}
  %\usepackage[UTF-8]{inputenc}
---

## Installation

The easiest way to install is from the development version from Github:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("MGallow/statr")
```

If there are any issues/bugs, please let me know: [github](https://github.com/MGallow/statr/issues). You can also contact me via my [website](http://users.stat.umn.edu/~gall0441/).

## Overview

`statr` is a personal R package that I have created for organizational/convenience purposes. This project is purely experimental!!! A (possibly incomplete) list of functions contained in the package can be found below:

* `tidy()` tidy's R package code and updates documentation
* `CVsplit()` splits data objects into training and testing sets
* `data_gen()` generates data for linear regression settings
* `dense()` generates dense matrices
* `denseQR()` generates dense matrices via spectral decomposition
* `tridiag()` generates tri-diagonal matrices
* `derivative()` approximates the derivative for a given function
* `diagnostic()` creates diagnostic plots using ggplot (residual and QQ)
* `dsearch()` is a dichotomous search algorithm for minimizing a univariate function
* `bsearch()` is a bi-section search algorithm for minimizing a univariate function
* `LASSO()` calculates lasso regression coefficient with optimal tuning
* `RIDGE()` calculates ridge regression coefficient with optimal tuning
* `scatter()` creates a scatterplot using ggplot


## Functions

### `diagnostic()`

Similar to `scatter`, `diagnostic` creates diagnostic plots (residual and QQ) in ggplot:

```{r message = FALSE}

#create diagnostic plots
cars %>% diagnostic(speed, dist)

```


### `dsearch()`

`dsearch` is a dichotomous search algorithm that will minimize *univariate strictly pseudoconvex* functions. Let us consider the quadratic function centered at 0:

```{r message = FALSE}

#quadratic
x = seq(-5, 5, 0.1)
y = x^2
data = data.frame(x, y)
ggplot(data) + geom_line(mapping = aes(x, y, color = "red"), show.legend = FALSE) + ggtitle("y = x^2")

```

The minimum of this function clearly occurs at $x = 0$ but we will confirm that with the `dsearch` function.

```{r message = FALSE}

#first we define the quadratic function
g = function(x){x^2}

#dsearch
dsearch(g, -10, 10)

```
We can see that `dsearch` confirms the minimum occurs at the suggested point.


### `bsearch()`

`bsearch` is a bisection search algorithm that works very similarly to `dsearch`. The difference being that `bsearch` will find the *root* of the function -- that is, when the function is equal to zero. Therefore, if we want to again minimize the quadratic function, we need to input the *derivative* of the quadratic function to find its minimum (recall that local minima and maxima occur when the derivative/gradient is equal to zero).

```{r message = FALSE}

#derivative of quadratic
x = seq(-5, 5, 0.1)
dy = 2*x
data = data.frame(x, dy)
ggplot(data) + geom_line(mapping = aes(x, dy, color = "red"), show.legend = FALSE) + ggtitle("dy = 2x")

```


```{r message = FALSE}

#define the derivative of quadratic
dg = function(x){2*x}

#bsearch
bsearch(dg, -10, 10)

```
We can see that `bsearch` confirms the minimum occurs at $x = 0$.

### `scatter()`

This function simply streamlines the process of creating a scatterplot with ggplot:

```{r message = FALSE}

#create scatterplot
cars %>% scatter(speed, dist)

```
